### 2017-06-05 paper/documents/4.experiment.tex
* caption in table using small caps, according to IEEE should be all caps, but looks ugly

\begin{table}[]
\centering
\begin{tabular}{|l|c|}
\hline
\rowcolor[HTML]{BBDAFF} 
\multicolumn{1}{|c|}{\cellcolor[HTML]{BBDAFF}\textbf{Attribute}} & \textbf{Number of Folds} \\ \hline
KDA Ratio* = (Kills + Assists) / (Deaths + 1)                    & 10                       \\ \hline
\rowcolor[HTML]{FFFFC7} 
Last Hits*                                                       & 10                       \\ \hline
Early Ganks*+                                                    & 10                       \\ \hline
\rowcolor[HTML]{FFFFC7} 
Number of Support Items*+                                        & 10                       \\ \hline
Damage to Neutral Creeps*+                                       & 10                       \\ \hline
\rowcolor[HTML]{FFFFC7} 
Damage to Regular Creeps*+                                       & 10                       \\ \hline
Lane Partners*+                                                  & 10                       \\ \hline
\rowcolor[HTML]{FFFFC7} 
Kills*                                                           & 9                        \\ \hline
Experience*                                                      & 5                        \\ \hline
\rowcolor[HTML]{FFFFC7} 
Deaths*                                                          & 5                        \\ \hline
Assists                                                          & 5                        \\ \hline
\rowcolor[HTML]{FFFFC7} 
Team Fight Participation*+                                       & 4                        \\ \hline
Early Movement (Visited Cells)*+                                 & 4                        \\ \hline
\rowcolor[HTML]{FFFFC7} 
Damage to Heroes*+                                               & 4                        \\ \hline
Solo Lane+                                                       & 2                        \\ \hline
\rowcolor[HTML]{FFFFC7} 
Damage to Towers+                                                & 1                        \\ \hline
Chosen Hero                                                      & 0                        \\ \hline
\rowcolor[HTML]{FFFFC7} 
Gold                                                             & 0                        \\ \hline
\end{tabular}
\caption{Attributes evaluated for classification. Attributes marked with + are not directly
available from replays. Attributes marked with {*} were finally selected for classification.
Number of Folds shows in how many folds an attribute was selected by WEKA’s
WrapperSubsetEval class using 10-fold cross-validation for each classification.}
\label{table:table1}
\end{table}

>>>>

\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{12pt}
\begin{table}[]
\caption{Attributes evaluated for classification. Attributes marked with + are not directly available from replays. Attributes marked with {*} were finally selected for classification. Number of Folds shows in how many folds an attribute was selected by WEKA’s WrapperSubsetEval class using 10-fold cross-validation for each classification.}
\label{table:table1}
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Attribute}                            & \textbf{Number of Folds} \\ \hline
KDA Ratio* = (Kills + Assists) / (Deaths + 1) & 10                       \\ \hline
Last Hits*                                    & 10                       \\ \hline
Early Ganks*+                                 & 10                       \\ \hline
Number of Support Items*+                     & 10                       \\ \hline
Damage to Neutral Creeps*+                    & 10                       \\ \hline
Damage to Regular Creeps*+                    & 10                       \\ \hline
Lane Partners*+                               & 10                       \\ \hline
Kills*                                        & 9                        \\ \hline
Experience*                                   & 5                        \\ \hline
Deaths*                                       & 5                        \\ \hline
Assists                                       & 5                        \\ \hline
Team Fight Participation*+                    & 4                        \\ \hline
Early Movement (Visited Cells)*+              & 4                        \\ \hline
Damage to Heroes*+                            & 4                        \\ \hline
Solo Lane+                                    & 2                        \\ \hline
Damage to Towers+                             & 1                        \\ \hline
Chosen Hero                                   & 0                        \\ \hline
Gold                                          & 0                        \\ \hline
\end{tabular}
\end{table}
